Enhancement of SDR in Thessaloniki

### 2024-06-05 GHI_enh_04_investigate.tex
Commit 2024-06-04 20:14
Commit 2024-06-05 19:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-04}

@@

@@

@@

\begin{verbatim}
2024-06-04 15:58:17.7 athan@tyler GHI_enh_04_investigate.R 2.098396 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-05}

@@

\begin{verbatim}
GLB_diff.sumPOS wattGLB.N  All_N
          <num>     <int>  <int>
\end{verbatim}

1: 3173.039 141910 199083
2: 6310.134 205953 266252
3: 6472.142 194258 266281
4: 6358.752 196986 266833
5: 7519.146 203571 266271
6: 7303.386 199796 266242
7: 6537.694 209089 266279
8: 6666.833 204624 266836
9: 8305.434 193973 266273
10: 8407.637 205622 266249
11: 6028.173 205861 266274
12: 8499.016 202060 266836
13: 10136.909 193257 266277
14: 10177.418 190648 266260
15: 8198.753 185166 266267
16: 6885.184 207421 266837
17: 8875.608 190199 266275
18: 12048.958 158225 266263
19: 8051.621 198105 266266
20: 6440.105 199732 266829
21: 9768.023 205393 266283
22: 13165.957 202673 266272
23: 9065.769 190944 266263
24: 12366.395 211300 266771
25: 10233.159 210016 266195
26: 9323.758 209719 266182
27: 8790.709 202142 266154
28: 9263.675 199167 266734
29: 9272.453 211799 266203
30: 7097.597 209101 266156
31: 10248.966 205824 265971
GLB\_diff.sumPOS wattGLB.N All\_N

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-4} \end{center}

@@

\begin{verbatim}
2024-06-05 15:58:36.8 athan@tyler GHI_enh_04_investigate.R 1.238620 mins
\end{verbatim}
